---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RAmP (R package for the Analysis of [modified] Proteomes)

<!-- badges: start -->
<!-- badges: end -->

The goal of RAmP is to perform a one-stop proteomic and PTM-proteomic analysis. It also includes differential expression analysis using limma, imputation and filtering options (from DEP), batch corrections, PCA and other quality control options. It also includes post-analysis visualization tools such as volcano plots, heatmaps, GO term analysis (both ORA and GSEA), KEGG analysis and corresponding visaulizations and motif search for PTM-based proteomics.

## Installation

You can install the development version of RAmP from [GitHub](https://github.com/anuroopv/RAmP) with:

``` {r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("anuroopv/RAmP", dependencies = TRUE)
library(RAmP)
```
Please note that RAmP requires an R version higher than 4.3.1. Please intsall the latest R version to avoid any compatibility issues with dependent packages. 

## Accessimg the data

Example proteome and acetylome data from Venkatasubramani AV, et al., 2023 (PMID: 37724628) can be accessed using:

``` r
data("sampleTable")
data("fasta")
data("protData")
data("enrichedData")
```

## Further information

For more information about RAmP, check the website: https://github.com/anuroopv/RAmP or refer to the help options after installation.


